Dynamic capabilities and competitive advantage

### 2019-10-25 article4_jbr.rnw
first chapter of paper 4 on non behavior

%https://www.gnu.org/software/emacs/manual/html_node/emacs/Fill-Commands.html
%https://academic.oup.com/journals/pages/authors/latex_files
%latexmk -pdf -pvc -auxdir=/Users/larshovdanmolden/Documents/Output/  article2_mancap.tex

@@

>>>>

% https://www.gnu.org/software/emacs/manual/html_node/emacs/Fill-Commands.html
%https://academic.oup.com/journals/pages/authors/latex_files
%latexmk -pdf -pvc -auxdir=/Users/larshovdanmolden/Documents/Output/  article2_mancap.tex

@@

Extant literature on dynamic capabilities are increasingly focusing on how firm resources
are changed by dynamic capabilities as a response to changes in the environment
\citep{Schilke2018,Eriksson2014}, thus placing firm resources as a mediator between
dynamic capabilities and competetive advantage \citep{Helfat2007}. Less focus has been
placed on the nature of these underlying firm resources (ref) and how they are capturing a
rather heterogeneous bulk of routines, capabilities, assets and capital. Hence, there is a
need to disentangle the black box of firm resources to provide a more nuanced
understanding of different types of firm resources and how they interact to shape firm
competitive advantage \cite{Schilke2018}. Indeed, this gap in the literature is explicitly
called by \cite{Schilke2018} where they  'see an interesting opportunity for future work to add greater richness to our
understanding of the mechanism of resource-base change, given this mechanism’s central
role in many foundational works (..) and the diverse ways in which resource changes can
potentially come about' (p. 419).

We aim to contribute to bridging this gap by

The inclusion of theoretical linkages of this sort appears to be important at this time
not only because they are at least partially overlooked in our current understanding of
capa- bility dynamics.

we propose a model that can accommodate the diverse nature of DCs with respect to the
objects of change that they aim to act upon and can better serve the call for a better
understanding of micro-foundations of strategy.

DCs required to adapt the more tacit and subtle aspect of human interactions (motivation,
emotions, and identity, in partic- ular) to environmental or contextual requirements

A dynamic capability is the capacity of an organization to purposefully create, extend or
modify its resource base. The resource base of an organization includes tangible,
intangible and human assets (or resources) as well as capabilities which the organization
owns, controls or has access to on a preferential basis.  (Helfat
